### 2021-07-10 src/paper/data/rapid_test_demand.tex
Continue extending the fit section.

>>>>

All shares of individuals who would take a rapid test if the conditions were met can be
seen in Figure~\ref{fig:rapid_test_demand}.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/data/testing/rapid_test_demand_shares}
    \caption{\textbf{Share of Individuals Doing a Rapid Test.}}
    \floatfoot{\noindent \textit{Note:} Rapid test demand can be triggered by individuals
    planning to have education contacts, work contacts, developing symptoms without
    access to a PCR test, having a household member with a positive test or symptoms. In
    each case whether a rapid test is done depends on how long it has been since the
    individual's last rapid test and her individual compliance parameters. As an example,
    take a worker in May. In that time workers are encouraged to test themselves twice
    weekly but there is no general requirement to test themselves. If the worker has not
    done a test within the last four days in our model she will demand a test if her
    (time-constant) compliance parameter belongs to the upper 60\% in the population.}
    \label{fig:rapid_test_demand}
\end{figure}

\begin{figure}[ht]
    \centering
    \caption{Share of Individuals With Rapid Tests}
    \label{fig:share_ever_rapid_test}
    \begin{subfigure}{.55\textwidth}
        \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_ever_rapid_test}
        \caption{Share of Individuals That Have Ever Done a Rapid Test}
    \end{subfigure}%
    \begin{subfigure}{.55\textwidth}
        \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_rapid_test_in_last_week}
        \caption{Share of Individuals Having Done a Rapid Test in the Last Week}
    \end{subfigure}
    \label{fig:share_rapid_test_last_week}
    \floatfoot{\noindent \textit{Note:} The figure compares the share of individuals who
        have ever done a rapid test or done a rapid test within the last week in our
        simulations to the shares reported in the
        \href{https://projekte.uni-erfurt.de/cosmo2020/web/topic/wissen-verhalten/80-schnelltests/}{COVID-19
        Snapshot Monitoring Survey}. The left panel compares the share of individuals who
        have ever done a rapid test. The right panel compares the share of individuals
        who have done a rapid test within the last seven days in our simulation compared
        to the share reporting to have done at least weekly rapid tests in the last four
        weeks in the COSMO survey. Overall our calibration of rapid tests are slightly
        conservative. The overall share is below that in the study. We fit the share of
        weekly tests quite exactly. However, the study only covers adults while our share
        also includes children who are tested very regularly when attending school.}
\end{figure}

 \comment[id=K]{J: Explain that we don't fit the share ever tested that well because our rapid test compliance is completely fixed. }

\FloatBarrier

### 2021-07-10 src/paper/results/fit.tex
Continue extending the fit section.

% observed infections

@@

\textcolor{red}{...} High levels of infections often coincide with increased statistical
uncertainty, as for example in April and May.

@@

\textcolor{red}{...} One important exception are the 80 to 100 year olds where we do not
fit the large number of cases in the winter of 2020/2021. This is because we do not model
nursing homes where a large fraction of this age group lives and a very large fraction of
cases in that age group occurred.

@@

Our states are uniform with respect to their age distribution. \textcolor{red}{...}

>>>>

% observed infections
Our fit of the infection rates in Germany between October 2020 and June 2021 is very
good. The incidence in our model follows the shape of the reported incidence almost
perfectly. The increase in December is somewhat less steep than it was. This can be
attributed to the large number of cases in nursing homes during that time that our model
cannot capture because it does not include nursing homes. It is very noticeable that high
levels of infections often coincide with increased statistical uncertainty, as for
example in April and May.

@@

% observed infections by age group
Zooming into the different age groups in Figure~\ref{fit:age_group_fit}, we can see that
our model is also able to reproduce the infection rates on this level. Differences
between the age groups allow us to identify the infection probabilities because different
age groups have contacts of different types (e.g. Mostly children go to school, the share
of workers is highest in the 35 to 59 age bracket etc.). There are three exceptions to
our fit. Firstly, the age group of 80 to 100 year olds due to the absence of nursing
homes in our synthetic population. Secondly, the increase in adolescents in April. It is
surprising that we do not match this increase despite explicitly modeling the
introduction of rapid tests for students. However, it can be expected that every rapid
test in a school setting is followed up by a PCR test while only 82\% of our population
\citep{Betsch2021} demand a confirming PCR test when receiving a positive rapid test. The
last age group where our fit does not fit the empirical curve very well is the group of
15 to 34 year olds. This group has been touted to have a very active social life and it
has often been suspected that this age group also stayed more socially active during the
pandemic. Since our model does not include either effect it's unsurprising that the
actual case numbers in this group are consistently higher than our simulated case
numbers.\comment[id=K]{Does anyone have an idea why we do not match the shape from Oct to
Dec?}

@@

% observed infections by federal state
Looking at another disaggr
Our states are uniform with respect to their age distribution.

@@
